Parsing Postfix log files

### 2008-02-10 doc/logparser.tex
Documented the parsing and verification of a random sample of log lines.

Warnings are issued for any lines which are not parsed; no warnings are
issued for unparsed lines while testing with the \numberOFlogFILES{} test
log files, so it can be safely concluded that there are zero false
negatives.  False positives are harder to quantify: short of examining each
of the 60,721,709 log lines and determining which \regex{} parsed it, there
is no way to be sure that every line was parsed by the correct \regex{},
making it impossible to quantify the false positive rate.  The author is
confident that the false positive rate is extremely low, approaching if not
reaching zero, because the \regexes{} used are as specific as possible and
care has been taken to ensure that there are no unintentionally overlapping
\regexes{}.

>>>>

Warnings are issued for any lines which are not parsed; no warnings are
issued for unparsed lines while testing with the \numberOFlogFILES{} test
log files, so it can be safely concluded that there are zero false
negatives.  False positives are harder to quantify: short of examining each
of the 60,721,709 log lines and determining which \regex{} parsed it, there
is no way to be sure that every line was parsed by the correct \regex{},
making it impossible to quantify the false positive rate; however a random
sample of 6039 log lines was parsed and the results checked manually to
ensure that the correct \regex{} parsed each line.  The sample was
generated by running the following command:

\verb!    perl -e 'print if (rand 1 < 0.0001)' -n LOG_FILES!

\noindent{}to randomly extract roughly one line in every 10,000.  Although
on initial appearances exercising only 36 rules (from a total of
\numberOFrules{}) when parsing 6039 log lines seems quite low, after
examining graph~\refwithpage{rule hits graph} it becomes apparent that such
a low hit rate is to be expected; the reader should also bear in mind that
even when parsing all \numberOFlogFILES{} log files not all the rules are
exercised (some of the rules are for parsing log lines which only appear in
other log files).
